Supplement to ``{\mytitle}''

### 2023-09-05 si/calibrateMod3.Rnw
new Makefile for creating supplement material

\begin{figure}[!h]
<<h3UnitLikes, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:h3UnitLikes}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!h]
<<CondLLFig, echo=FALSE, message=FALSE, fig.height=3>>=

@@

\begin{figure}[!h]
<<finalCondLLFig, echo=FALSE, message=FALSE, fig.height=3>>=
t(bpf_final3_out$block.cond.loglik) %>%
  as.data.frame() %>%
  mutate(t = bpf_final3_out$times) %>%
  pivot_longer(
    cols = -t,
    values_to = 'likelihood',
    names_prefix = "V",
    names_to = 'Unit'
  ) %>%
  mutate(date = as.Date(lubridate::date_decimal(t))) %>%
  ggplot(aes(x = date, y = likelihood)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Unit, labeller = myLabeller, scales = 'free_y',
             nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = -45, hjust = 0)) +
  ylab("Conditional log-likelihoods")
@
\caption{\label{fig:finalCondLL}Conditional log-likelihoods of Model~3 after adding and estimating the parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!h]
<<finalUnitLLFig, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:finalUnitLL}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model after adding and estimating parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!h]
<<h3SusFig, echo=FALSE, message=FALSE, fig.height=3>>=
ggplot() +
  # Sims from initial condition
  geom_line(data = h3Spat_quants, aes(x = date, y = Q50), col = 'red') +
  geom_ribbon(
    data = h3Spat_quants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'red', alpha = 0.5
  ) +
  # projections from initial condition, using filtered sims function
  geom_line(data = mod3_V0_initcond_res$SQuants, aes(x = date, y = Q50), col = 'red') +
  geom_ribbon(
    data = mod3_V0_initcond_res$SQuants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'red', alpha = 0.5
  ) +
  # Sims from filtered distribution
  geom_line(
    data = bpf_final3_out$Sus_df,
    aes(x = as.Date(lubridate::date_decimal(time)), y = Q50),
    col = 'blue'
  ) +
  geom_ribbon(
    data = bpf_final3_out$Sus_df,
    aes(x = as.Date(lubridate::date_decimal(time)), ymin = Q025, ymax = Q975),
    fill = 'blue', alpha = 0.5
  ) +
  # Projections from filtered distribution
  geom_line(data = mod3_V0_res$SQuants, aes(x = date, y = Q50), col = 'blue') +
  geom_ribbon(
    data = mod3_V0_res$SQuants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'blue', alpha = 0.5
  ) +
  geom_vline(xintercept = max(h3Spat_quants$date), linetype = 'dashed') +
  facet_wrap(~dep, scales = 'free_y', nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = -45, hjust = 0)) +
  ylab("Total Susceptible (%)")
@
\caption{\label{fig:h3Sus}Percentage of individuals that are in the susceptible compartment.
Simulations from Model~3 under initial conditions are displayed in red; simulations from the filtering distribution of model are displayed in blue.
The dashed line represents the end of the observed data.}
\end{figure}

>>>>

\begin{figure}[!ht]
<<h3UnitLikes, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:h3UnitLikes}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
<<CondLLFig, echo=FALSE, message=FALSE, fig.height=3>>=

@@

\begin{figure}[!ht]
<<finalCondLLFig, echo=FALSE, message=FALSE, fig.height=3>>=
t(bpf_final3_out$block.cond.loglik) %>%
  as.data.frame() %>%
  mutate(t = bpf_final3_out$times) %>%
  pivot_longer(
    cols = -t,
    values_to = 'likelihood',
    names_prefix = "V",
    names_to = 'Unit'
  ) %>%
  mutate(date = as.Date(lubridate::date_decimal(t))) %>%
  ggplot(aes(x = date, y = likelihood)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Unit, labeller = myLabeller, scales = 'free_y',
             nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = -45, hjust = 0)) +
  ylab("Conditional log-likelihoods")
@
\caption{\label{fig:finalCondLL}Conditional log-likelihoods of Model~3 after adding and estimating the parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
<<finalUnitLLFig, fig.height=3, fig.width=5.5, echo=FALSE>>=
ggplot(bench_M3_joined, aes(x = ll, y = reorder(unit, ll))) +
  geom_point(aes(col = type)) +
  ylab("Unit") +
  xlab("Log Likelihood") +
  scale_color_manual(
    labels = c("ll" = "Benchmark", "ll_est" = "Model 3"),
    values = c("ll" = "#1b9e77", "ll_est" = "#d95f02")
  ) +
  theme(legend.title = element_blank(),
        axis.title.y = element_blank())
@
\caption{\label{fig:finalUnitLL}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model after adding and estimating parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
<<h3SusFig, echo=FALSE, message=FALSE, fig.height=3>>=
ggplot() +
  # Sims from initial condition
  geom_line(data = h3Spat_quants, aes(x = date, y = Q50), col = 'red') +
  geom_ribbon(
    data = h3Spat_quants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'red', alpha = 0.5
  ) +
  # projections from initial condition, using filtered sims function
  geom_line(data = mod3_V0_initcond_res$SQuants, aes(x = date, y = Q50), col = 'red') +
  geom_ribbon(
    data = mod3_V0_initcond_res$SQuants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'red', alpha = 0.5
  ) +
  # Sims from filtered distribution
  geom_line(
    data = bpf_final3_out$Sus_df,
    aes(x = as.Date(lubridate::date_decimal(time)), y = Q50),
    col = 'blue'
  ) +
  geom_ribbon(
    data = bpf_final3_out$Sus_df,
    aes(x = as.Date(lubridate::date_decimal(time)), ymin = Q025, ymax = Q975),
    fill = 'blue', alpha = 0.5
  ) +
  # Projections from filtered distribution
  geom_line(data = mod3_V0_res$SQuants, aes(x = date, y = Q50), col = 'blue') +
  geom_ribbon(
    data = mod3_V0_res$SQuants,
    aes(x = date, ymin = Q025, ymax = Q975),
    fill = 'blue', alpha = 0.5
  ) +
  geom_vline(xintercept = max(h3Spat_quants$date), linetype = 'dashed') +
  facet_wrap(~dep, scales = 'free_y', nrow = 2) +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = -45, hjust = 0)) +
  ylab("Total Susceptible (%)")
@
\caption{\label{fig:h3Sus}Percentage of individuals that are in the susceptible compartment.
Simulations from Model~3 under initial conditions are displayed in red; simulations from the filtering distribution of model are displayed in blue.
The dashed line represents the end of the observed data.}
\end{figure}
